---
title: "Step4_Model Selection GLMMs"
author: "Billy Geary"
date: "16/09/2021"
output: html_document
---

# SETUP
Analysis document for Upper Warren dynamic occupancy models for feral cat and red fox in response to a range of covariates, mostly rain, baiting intensity and distance to ag. 

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
library(unmarked)
library(dplyr)
library(lme4)
library(ggplot2)
library(cowplot)
library(ggeffects)
library(MuMIn)
```


## Load the Unmarked Occupancy Frames

```{r, message=FALSE, warning=FALSE}
load("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Data_Clean/foxes.umf.16092021.Rda")
load("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Data_Clean/cats.umf.16092021.Rda")

# Create a year covariate
foxes.umf@siteCovs$Year = lubridate::year(foxes.umf@siteCovs$Date)
cats.umf@siteCovs$Year = lubridate::year(cats.umf@siteCovs$Date)

# Create a BACI covariate
foxes.umf@siteCovs = foxes.umf@siteCovs %>% 
  mutate(YEAR_GROUPS = ifelse(Year < 2009, "2006_2008",
                              ifelse(Year >2008 & Year < 2011, "2009_2010", "2011_2013"))) %>% 
  mutate(Year = as.factor(Year),
         YEAR_GROUPS = as.factor(YEAR_GROUPS)) 
         
summary(foxes.umf)

# Create a BACI covariate
cats.umf@siteCovs = cats.umf@siteCovs %>% 
  mutate(YEAR_GROUPS = ifelse(Year < 2009, "2006_2008",
                              ifelse(Year >2008 & Year < 2011, "2009_2010", "2011_2013"))) %>% 
  mutate(Year = as.factor(Year),
         YEAR_GROUPS = as.factor(YEAR_GROUPS)) 
         
```


## Create RepRate Data Frame
```{r}
fox.dat = data.frame(FoxCount =  apply(foxes.umf@y, 1, sum, na.rm=TRUE),
                     Effort = rowSums(!is.na(foxes.umf@y)))
fox.dat$FoxRR = fox.dat$FoxCount/fox.dat$Effort
cat.dat = data.frame(CatCount =  apply(cats.umf@y, 1, sum, na.rm=TRUE))

count.data = cbind(fox.dat, cat.dat, cats.umf@siteCovs)
count.data$CatRR = count.data$CatCount/count.data$Effort

count.data = filter(count.data, Effort !=0)

count.data$DaysSinceStart = as.numeric(count.data$Date - min(count.data$Date)) 
```

# Plot Proportion of sites occupied over time
```{r}
occ.plot = count.data %>%
  mutate(FoxPA = ifelse(FoxRR > 0, 1, 0),
         CatPA = ifelse(CatRR >0, 1, 0)) %>%
  group_by(Transect, Session) %>% summarise(FoxOcc = sum(FoxPA)/50, CatOcc = sum(CatPA)/50) %>%
  ggplot() + geom_line(aes(x = Session, y = FoxOcc, colour="Red Fox")) + geom_line(aes(x = Session, y = CatOcc, colour = "Feral Cat")) + 
  facet_wrap(~Transect) + ylab("Proportion of Sites Occupied") + theme_cowplot() +
  scale_colour_manual(name = "Species",
                      labels = c("Feral Cat", "Red Fox"), values=c("#3B528BFF","#5DC863FF")) 

```

# Plot Reporting Rates
```{r}
rep.plot = ggplot(count.data) + 
  geom_point(aes(x=Date, y=FoxRR, colour="Red Fox"), alpha=0.4, position = 'jitter') +
  geom_point(aes(x=Date, y=CatRR, colour="Feral Cat"), alpha=0.4, position='jitter') +
  geom_smooth(aes(x=Date, y=FoxRR, fill="Red Fox", colour="Red Fox"), method='gam', 
              formula=y~s(x, k=5), method.args= list(family='binomial')) +
  geom_smooth(aes(x=Date, y=CatRR, fill="Feral Cat", colour="Feral Cat"), method='gam', 
              formula=y~s(x,k=5), method.args= list(family='binomial')) +
  facet_wrap(~Transect) + ylab("Reporting Rate") +
  theme_cowplot() +
  scale_colour_manual(name = "Species",
                     labels = c("Feral Cat", "Red Fox"), values=c("#3B528BFF","#5DC863FF")) + 
  scale_fill_manual(name = "Species",
                     labels = c("Feral Cat", "Red Fox"), values=c("#3B528BFF","#5DC863FF")) 

rep.plot

ggsave("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/Fig2_reprate.pdf", plot=rep.plot, dpi=600, width=5, height=3, scale =2, units="in")
```

# Check for coliniarity between covariates
Dont want to include variables that have a correlation of more than +/-0.5, which looks like we're all good. 
```{r, message=FALSE, warning=FALSE, fig.width=9}
cors = count.data %>% 
  dplyr::select(Rain_TwelveMonths, DistAg, MeanBaitIntensity_Twelve, Prey_Twelve, FoxRR) %>%
  setNames(c("Precipitation", "DistToAgriculture", "FoxBaitingIntensity", "PreyAbundance", "FoxActivity")) %>%
  cor(method = "spearman") %>% round(digits=2) %>% as.data.frame() 
```


# RED FOX
H1: An increase in baiting intensity leads to a decline in foxes 
H2: A change in baiting intensity to target foxy areas did this
H3: Foxes are driven by stochastic variation between years which affects the effectiveness of baiting intensity
H4: Foxes are driven more by prey than by baiting intensity or rainfall
H5: An increase in baiting intensity leads to a decline in foxes but only in dry years because in wet years foxes are reproducing a lot and new ones are dispersing straight back into the site after foxes are killed 

## Test for temporal autocorrelation
```{r}
fox.temp = glmer(cbind(FoxCount, Effort - FoxCount) ~ (1|Site) + (1|Year), data=count.data, family = 'binomial')
summary(fox.temp)
E <- residuals(fox.temp)
I1 <- !is.na(count.data$FoxCount)
Efull <- vector(length=length(count.data$FoxCount))
Efull[I1]<-E
acf(Efull, na.action=na.pass, main="Autocorrelation Plot")

```

```{r}
cat.temp = glmer(cbind(CatCount, Effort - CatCount) ~ Session + (1|Site) + (1|Year), data=count.data, family = 'binomial')
summary(cat.temp)
E <- residuals(cat.temp)
I1 <- !is.na(count.data$CatCount)
Efull <- vector(length=length(count.data$CatCount))
Efull[I1]<-E
acf(Efull, na.action=na.pass, main="Autocorrelation Plot")
```

```{r}
fox.temp = glmer(cbind(FoxCount, Effort - FoxCount) ~ Session + (1|Site), data=count.data, family = 'binomial', correlation = corCompSymm(form=~Session))

fox.gam = mgcv::gam()


fox = brm(FoxCount| trials(Effort) ~ (1|Site), data=count.data, family = 'binomial')

fox.global = brm(FoxCount| trials(Effort) ~ 
                       scale(Rain_TwelveMonths) +
                       scale(DistAg) +
                       scale(MeanBaitIntensity_Twelve) +
                       scale(Prey_Twelve) + (1|Site), data=count.data, family = 'binomial', cores=4)

fox.global.temp = brm(FoxCount| trials(Effort) ~ 
                       scale(Rain_TwelveMonths) +
                       scale(MeanBaitIntensity_Twelve) +
                       scale(Prey_Twelve) + 
                       arma(time=Session, gr=Site, cov=TRUE), data=count.data, family = 'binomial', cores=4)

fox.int = brm(FoxCount| trials(Effort) ~ 
                       scale(MeanBaitIntensity_Twelve) *
                       scale(Prey_Twelve) + 
                       arma(time=Session, gr=Site, cov=TRUE), data=count.data, family = 'binomial', cores=4)


WAIC(fox.global, fox.global.temp, fox)

best.fox.model = fox.global.temp

df = data.frame(Rain_TwelveMonths = seq(min(count.data$Rain_TwelveMonths), max(count.data$Rain_TwelveMonths), 5),
                                   MeanBaitIntensity_Twelve = mean(count.data$MeanBaitIntensity_Twelve),
                                   Prey_Twelve = mean(count.data$Prey_Twelve), Site=NA, Effort=max(count.data$Effort))

a.pred = df %>% tidybayes::add_epred_draws(best.fox.model, re_form=NA, incl_autocor = FALSE, summary=TRUE)

a.pred.mean = a.pred %>% group_by(Rain_TwelveMonths) %>% summarise(Mean = mean(.epred))

a= ggplot() +
  geom_line(aes(x = a.pred$Rain_TwelveMonths, y = a.pred$.epred, group = a.pred$.draw), alpha = 0.1) +
  geom_line(aes(x = a.pred.mean$Rain_TwelveMonths, y = a.pred.mean$Mean), color = "red", lwd = 2)




df = data.frame(MeanBaitIntensity_Twelve = seq(min(count.data$MeanBaitIntensity_Twelve), max(count.data$MeanBaitIntensity_Twelve), 0.1),
                                   Rain_TwelveMonths = mean(count.data$Rain_TwelveMonths),
                                   Prey_Twelve = mean(count.data$Prey_Twelve), Site=NA, Effort=max(count.data$Effort))
b.pred = df %>% tidybayes::add_epred_draws(best.fox.model, re_form=NA, incl_autocor = FALSE, summary=TRUE)

b.pred.mean = b.pred %>% group_by(MeanBaitIntensity_Twelve) %>% summarise(Mean = mean(.epred))
b= ggplot() +
  geom_line(aes(x = b.pred$MeanBaitIntensity_Twelve, y = b.pred$.epred, group = b.pred$.draw), alpha = 0.1) +
  geom_line(aes(x = b.pred.mean$MeanBaitIntensity_Twelve, y = b.pred.mean$Mean), color = "red", lwd = 2)



df= data.frame(Prey_Twelve = seq(min(count.data$Prey_Twelve), max(count.data$Prey_Twelve), 0.02),
                                   MeanBaitIntensity_Twelve = mean(count.data$MeanBaitIntensity_Twelve),
                                   Rain_TwelveMonths = mean(count.data$Rain_TwelveMonths),Site=NA, Effort=max(count.data$Effort))

c.pred = df %>% tidybayes::add_epred_draws(best.fox.model, re_form=NA, incl_autocor = FALSE, summary=TRUE)

c.pred.mean = c.pred %>% group_by(Prey_Twelve) %>% summarise(Mean = mean(.epred))
c= ggplot() +
  geom_line(aes(x = c.pred$Prey_Twelve, y = c.pred$.epred, group = c.pred$.draw), alpha = 0.1) +
  geom_line(aes(x = c.pred.mean$Prey_Twelve, y = c.pred.mean$Mean), color = "red", lwd = 2)


fox.panel = cowplot::plot_grid(a,b,c, labels=c("a)","b)","c)"), nrow=1)


```

## Fit some GLMMs
### Question 1
```{r}
fox.global.model = mgcv::gam(cbind(FoxCount, Effort-FoxCount) ~ 
                       scale(Rain_TwelveMonths) +
                       scale(DistAg) +
                       scale(MeanBaitIntensity_Twelve) +
                       scale(Prey_Twelve),
                       correlation = corAR1(form = ~ Session|Site),  
                       data = count.data, family = binomial)


options(na.action = "na.fail")
fox.dredged.models =  MuMIn::dredge(fox.global.model, rank="AICc")


best.fox.model = mgcv::gam(cbind(FoxCount, Effort-FoxCount) ~ 
                       scale(Rain_TwelveMonths) +
                       scale(MeanBaitIntensity_Twelve) +
                       scale(Prey_Twelve),
                       correlation = corAR1(form = ~ Session|Site),  
                       data = count.data, family = binomial)

summary(best.fox.model)

r.squaredGLMM(best.fox.model)

coefs = data.frame(Coef = summary(best.fox.model)$p.coeff)
se = data.frame(SE = summary(best.fox.model)$se)
coefs = cbind(coefs, se)
coefs$lci = coefs$Coef - coefs$SE*1.96
coefs$uci = coefs$Coef + coefs$SE*1.96
coefs$Model = "Fox"

write.csv(fox.dredged.models, "~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/FoxModelSel_03062022.csv")
```

#### Plot Results
```{r}
pred = data.frame(Rain_TwelveMonths = seq(min(count.data$Rain_TwelveMonths), max(count.data$Rain_TwelveMonths), 5),
                  MeanBaitIntensity_Twelve = mean(count.data$MeanBaitIntensity_Twelve),
                  Prey_Twelve = mean(count.data$Prey_Twelve))

prediction = predict(best.fox.model, newdata=pred, se.fit=TRUE, type="response")
pred$fit = prediction$fit
pred$se = prediction$se.fit

fox.a = ggplot(pred) + geom_ribbon(aes(x = Rain_TwelveMonths, ymin = fit-se*1.96, ymax=fit+se*1.96), alpha=0.4)+
  geom_line(aes(x=Rain_TwelveMonths, y = fit)) + 
  xlab("Rain in Previous Twelve Months (mm)") + ylab("Fox Reporting Rate") + theme_bw() +
  theme(plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) + ylim(c(0, 0.25))

pred = data.frame(MeanBaitIntensity_Twelve = seq(min(count.data$MeanBaitIntensity_Twelve), 
                                                 max(count.data$MeanBaitIntensity_Twelve), 0.1),
                                   Rain_TwelveMonths = mean(count.data$Rain_TwelveMonths),
                                   Prey_Twelve = mean(count.data$Prey_Twelve))
prediction = predict(best.fox.model, newdata=pred, se.fit=TRUE, type="response")
pred$fit = prediction$fit
pred$se = prediction$se.fit


fox.b = ggplot(pred) + geom_ribbon(aes(x = MeanBaitIntensity_Twelve, ymin = fit-se*1.96, ymax=fit+se*1.96), alpha=0.4)+
  geom_line(aes(x=MeanBaitIntensity_Twelve, y = fit)) + 
  xlab("Bait Intensity Previous Twelve Months (baits/km^2)") + ylab("Fox Reporting Rate") +theme_bw() +
  theme(plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) + ylim(c(0, 0.25))

pred = data.frame(Prey_Twelve = seq(min(count.data$Prey_Twelve), max(count.data$Prey_Twelve), 0.02),
                                   MeanBaitIntensity_Twelve = mean(count.data$MeanBaitIntensity_Twelve),
                                   Rain_TwelveMonths = mean(count.data$Rain_TwelveMonths))
prediction = predict(best.fox.model, newdata=pred, se.fit=TRUE, type="response")
pred$fit = prediction$fit
pred$se = prediction$se.fit


fox.c = ggplot(pred) + geom_ribbon(aes(x = Prey_Twelve, ymin = fit-se*1.96, ymax=fit+se*1.96), alpha=0.4)+
  geom_line(aes(x=Prey_Twelve, y = fit)) + xlab("Prey Abundance Index") + ylab("Fox Reporting Rate") + theme_bw() +
  theme(plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) + ylim(c(0, 0.25))


fox.panel = cowplot::plot_grid(fox.a,fox.b,fox.c, labels=c("a)","b)","c)"), nrow=1)

ggsave("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/Fig3_foxpanel_03062022.pdf", plot=fox.panel, dpi=600, width=5, height=1.5, scale =2, units="in")

```


### Question 2
```{r}
foxint.m1 = mgcv::gam(cbind(FoxCount, Effort-FoxCount) ~ 1, 
                      data = count.data, family = 'binomial', correlation = corAR1(form = ~ Session|Site))
foxint.m2 = mgcv::gam(cbind(FoxCount, Effort-FoxCount) ~ scale(MeanBaitIntensity_Twelve)*scale(Rain_TwelveMonths),
                      data = count.data, family = 'binomial', correlation = corAR1(form = ~ Session|Site))
foxint.m3 = mgcv::gam(cbind(FoxCount, Effort-FoxCount) ~ scale(MeanBaitIntensity_Twelve)*scale(Prey_Twelve),
                      data = count.data, family = 'binomial', correlation = corAR1(form = ~ Session|Site))
foxint.m4 = mgcv::gam(cbind(FoxCount, Effort-FoxCount) ~ scale(MeanBaitIntensity_Twelve)*scale(DistAg), 
                      data = count.data, family = 'binomial', correlation = corAR1(form = ~ Session|Site))


model.sel.fox = model.sel(foxint.m1, foxint.m2, foxint.m3, foxint.m4)
model.sel.fox
best.fox.model = mgcv::gam(cbind(FoxCount, Effort-FoxCount) ~ scale(MeanBaitIntensity_Twelve)*scale(Prey_Twelve),
                      data = count.data, family = 'binomial', correlation = corAR1(form = ~ Session|Site))

summary(best.fox.model)

r.squaredGLMM(best.fox.model)
coefs.int = data.frame(Coef = summary(best.fox.model)$p.coeff)
se = data.frame(SE = summary(best.fox.model)$se)
coefs.int = cbind(coefs.int, se)
coefs.int$lci = coefs.int$Coef - coefs.int$SE*1.96
coefs.int$uci = coefs.int$Coef + coefs.int$SE*1.96
coefs.int$Model = "Fox Int"

write.csv(model.sel.fox, "~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/FoxBaitModelSel_03062022.csv")

```


## Plot Results
```{r}
pred = data.frame(expand.grid(MeanBaitIntensity_Twelve = seq(min(count.data$MeanBaitIntensity_Twelve), 
                                                 max(count.data$MeanBaitIntensity_Twelve), 0.1),
                                   Prey_Twelve = quantile(count.data$Prey_Twelve, probs = c(0.10, 0.5, 0.90))))

prediction = predict(best.fox.model, newdata=pred, se.fit=TRUE, type="response")
pred$fit = prediction$fit
pred$se = prediction$se.fit
pred$Prey_Twelve = as.factor(round(pred$Prey_Twelve, digits=1))

fox.int = ggplot() + 
  geom_ribbon(aes(x=pred$MeanBaitIntensity_Twelve, ymin=pred$fit-1.96*pred$se, ymax=pred$fit+1.96*pred$se, fill=pred$Prey_Twelve), alpha=0.4) +
  geom_line(aes(x=pred$MeanBaitIntensity_Twelve, y=pred$fit, colour=pred$Prey_Twelve)) +
  #geom_point(aes(x=count.data$MeanBaitIntensity_Twelve, y=count.data$FoxRR)) + 
  xlab("Baiting Intensity prv 12 months (Baits/km^2)") + ylab("Fox Reporting Rate") +
  scale_color_viridis_d(name = "Prey Activity Index") +
  scale_fill_viridis_d(name = "Prey Activity Index") + theme_bw() +
  theme(plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) + ylim(c(0, 0.25))

pred = data.frame(expand.grid(Prey_Twelve = seq(min(count.data$Prey_Twelve), 
                                                 max(count.data$Prey_Twelve), 0.01),
                                   MeanBaitIntensity_Twelve = quantile(count.data$MeanBaitIntensity_Twelve, probs = c(0.10, 0.5, 0.90))))

prediction = predict(best.fox.model, newdata=pred, se.fit=TRUE, type="response")
pred$fit = prediction$fit
pred$se = prediction$se.fit
pred$MeanBaitIntensity_Twelve = as.factor(round(pred$MeanBaitIntensity_Twelve, digits=1))

fox.int = ggplot() + 
  geom_ribbon(aes(x=pred$Prey_Twelve, ymin=pred$fit-1.96*pred$se, ymax=pred$fit+1.96*pred$se, fill=pred$MeanBaitIntensity_Twelve), alpha=0.4) +
  geom_line(aes(x=pred$Prey_Twelve, y=pred$fit, colour=pred$MeanBaitIntensity_Twelve)) +
  #geom_point(aes(x=count.data$MeanBaitIntensity_Twelve, y=count.data$FoxRR)) + 
  xlab("Prey Activity Index") + ylab("Fox Reporting Rate") +
  scale_color_viridis_d(name = "Baiting Intensity (Baits/km^2)") +
  scale_fill_viridis_d(name = "Baiting Intensity (Baits/km^2)") + theme_bw() +
  theme(plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) + ylim(c(0, 0.25))


ggsave("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/Fig4_foxint_03062022.pdf", plot=fox.int, dpi=600, width=3.5, height=2, scale =1.5, units="in")
```

# FERAL CAT
## Temporal autocorrelation
```{r}

cat = brm(CatCount| trials(Effort) ~ (1|Site), data=count.data, family = 'binomial', cores=4)

cat.global = brm(CatCount| trials(Effort) ~ 
                       scale(Rain_TwelveMonths) +
                       scale(DistAg) +
                       scale(MeanBaitIntensity_Twelve) +
                       scale(Prey_Twelve) + (1|Site), data=count.data, family = 'binomial', cores=4)

cat.global.temp = brm(CatCount| trials(Effort) ~ 
                       scale(Rain_TwelveMonths) +
                       scale(MeanBaitIntensity_Twelve) +
                       scale(Prey_Twelve) + 
                       scale(FoxRR) + (1|Site) + (1|Year) +
                       arma(time=Session, gr=Site, cov=TRUE) + (1|Site), data=count.data, family = 'binomial', cores=4)

WAIC(cat.global, cat.global.temp, cat)

best.cat.model = cat.global.temp

df = data.frame(Rain_TwelveMonths = seq(min(count.data$Rain_TwelveMonths), max(count.data$Rain_TwelveMonths), 5),
                                   MeanBaitIntensity_Twelve = mean(count.data$MeanBaitIntensity_Twelve),
                                   FoxRR = mean(count.data$FoxRR),
                                   Prey_Twelve = mean(count.data$Prey_Twelve), Site=NA,Year=NA, Effort=1)

a.pred = df %>% tidybayes::add_epred_draws(best.cat.model, re_form=NA, incl_autocor = FALSE, summary=TRUE)

a.pred.mean = a.pred %>% group_by(Rain_TwelveMonths) %>% summarise(Mean = mean(.epred))

a= ggplot() +
  geom_line(aes(x = a.pred$Rain_TwelveMonths, y = a.pred$.epred, group = a.pred$.draw), alpha = 0.1) +
  geom_line(aes(x = a.pred.mean$Rain_TwelveMonths, y = a.pred.mean$Mean), color = "red", lwd = 2)




df = data.frame(MeanBaitIntensity_Twelve = seq(min(count.data$MeanBaitIntensity_Twelve), max(count.data$MeanBaitIntensity_Twelve), 0.1),
                                   Rain_TwelveMonths = mean(count.data$Rain_TwelveMonths),
                                   FoxRR = mean(count.data$FoxRR),
                                   Prey_Twelve = mean(count.data$Prey_Twelve), Site=NA, Effort=max(count.data$Effort))
b.pred = df %>% tidybayes::add_epred_draws(best.cat.model, re_form=NA, incl_autocor = FALSE, summary=TRUE)

b.pred.mean = b.pred %>% group_by(MeanBaitIntensity_Twelve) %>% summarise(Mean = mean(.epred))
b= ggplot() +
  geom_line(aes(x = b.pred$MeanBaitIntensity_Twelve, y = b.pred$.epred, group = b.pred$.draw), alpha = 0.1) +
  geom_line(aes(x = b.pred.mean$MeanBaitIntensity_Twelve, y = b.pred.mean$Mean), color = "red", lwd = 2)



df= data.frame(Prey_Twelve = seq(min(count.data$Prey_Twelve), max(count.data$Prey_Twelve), 0.02),
                                   MeanBaitIntensity_Twelve = mean(count.data$MeanBaitIntensity_Twelve),
                                   FoxRR = mean(count.data$FoxRR),
                                   Rain_TwelveMonths = mean(count.data$Rain_TwelveMonths),Site=NA, Effort=max(count.data$Effort))

c.pred = df %>% tidybayes::add_epred_draws(best.cat.model, re_form=NA, incl_autocor = FALSE, summary=TRUE)

c.pred.mean = c.pred %>% group_by(Prey_Twelve) %>% summarise(Mean = mean(.epred))
c= ggplot() +
  geom_line(aes(x = c.pred$Prey_Twelve, y = c.pred$.epred, group = c.pred$.draw), alpha = 0.1) +
  geom_line(aes(x = c.pred.mean$Prey_Twelve, y = c.pred.mean$Mean), color = "red", lwd = 2)


cat.panel = cowplot::plot_grid(a,b,c, labels=c("a)","b)","c)"), nrow=1)


```

## Fit some GLMMs
```{r}
cat.global.model = mgcv::gam(cbind(CatCount, Effort-CatCount) ~ 
                           scale(Rain_TwelveMonths)+
                           scale(FoxRR)+
                           scale(DistAg)+
                           scale(MeanBaitIntensity_Twelve)+
                           scale(Prey_Twelve),
                           data = count.data, family = 'binomial',  correlation = corAR1(form = ~ Session|Site))

options(na.action = "na.fail")
cat.dredged.models =  MuMIn::dredge(cat.global.model, rank="AICc")

best.cat.model = mgcv::gam(cbind(CatCount, Effort-CatCount) ~ 
                           scale(MeanBaitIntensity_Twelve)+
                           scale(Prey_Twelve),
                           data = count.data, family = 'binomial',  correlation = corAR1(form = ~ Session|Site))
summary(best.cat.model)
r.squaredGLMM(best.cat.model)

coefs.cat = data.frame(Coef = summary(best.cat.model)$p.coeff)
se = data.frame(SE = summary(best.cat.model)$se)
coefs.cat = cbind(coefs.cat, se)
coefs.cat$lci = coefs.cat$Coef - coefs.cat$SE*1.96
coefs.cat$uci = coefs.cat$Coef + coefs.cat$SE*1.96
coefs.cat$Model = "Cat"

write.csv(cat.dredged.models, "~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/CatModelSel_03062022.csv")


all.coefs = rbind(coefs, coefs.int, coefs.cat)
all.coefs$Predictor = rownames(all.coefs)

write.csv(all.coefs, "~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/CoefTable_03062022.csv")

```

## Plot Results
```{r}
pred = data.frame(MeanBaitIntensity_Twelve = seq(min(count.data$MeanBaitIntensity_Twelve),
                                                 max(count.data$MeanBaitIntensity_Twelve), 0.1),
                                   Prey_Twelve = mean(count.data$Prey_Twelve))

prediction = predict(best.cat.model, newdata=pred, se.fit=TRUE, type="response")
pred$fit = prediction$fit
pred$se = prediction$se.fit

cat.a = ggplot(pred) + geom_ribbon(aes(x = MeanBaitIntensity_Twelve, ymin = fit-se*1.96, ymax=fit+se*1.96), alpha=0.4)+
  geom_line(aes(x=MeanBaitIntensity_Twelve, y = fit)) + xlab("Bait Intensity Previous Twelve Months (baits/km^2)") + ylab("Cat Reporting Rate") + theme_bw() +
  theme(plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) + ylim(c(0, 0.17))


pred= data.frame(Prey_Twelve = seq(min(count.data$Prey_Twelve), max(count.data$Prey_Twelve), 0.02),
                 MeanBaitIntensity_Twelve = mean(count.data$MeanBaitIntensity_Twelve))
prediction = predict(best.cat.model, newdata=pred, se.fit=TRUE, type="response")
pred$fit = prediction$fit
pred$se = prediction$se.fit

cat.b = ggplot(pred) + geom_ribbon(aes(x = Prey_Twelve, ymin = fit-se*1.96, ymax=fit+se*1.96), alpha=0.4)+
  geom_line(aes(x=Prey_Twelve, y = fit)) + xlab("Prey Abundance Index") + ylab("Cat Reporting Rate") + theme_bw() +
  theme(plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) + ylim(c(0, 0.17))


cat.panel=cowplot::plot_grid(cat.a,cat.b,labels=c("a)","b)"), nrow=1)

ggsave("~/Dropbox/Billy/_research/_PhD/07_UpperWarren_WA/_Projects/upperwarren_foxcat/Outputs/Fig5_catpanel_03062022.pdf", plot=cat.panel, dpi=600, width=3, height=1.5, scale =2, units="in")
```
